---
title: "RCoding7"
author: "M. Lawrance"
date: '2023-05-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Load Packages
library(tidyverse)
library(dplyr)
library(fixest)
library(broom)
```

```{r}
#Let's set up a power analysis simulation function!

power_analyses  <- function(effect, sample_size, yvar, xmin, xmax) {
  coeff <- c() #Make a vector to store the coefficients
  significance <- c() #Make a vector to store the number of the coefficients that are significant
  
  for (i in 1:2000) {
    # Form the data structure using our inputs
    tib <- tibble(
      X = runif(sample_size, xmin, xmax) #samplesize and the ranges of values expected from our predictor value
    ) %>%
      mutate(Y = effect*X + rnorm(sample_size, mean = 0, sd = yvar)) # derive Y from X based on our expected effect size, plus                                                                           the variance of our y value
    
    # Run the analysis
    model <- feols(Y ~ X, data = tib, se = 'hetero')
    
    # Return the results
    coeff[i] <- coef(model)[2]
    significance[i] <- tidy(model)$p.value[2] <= .05
  }
    significance %>%
    mean() %>%
    return()
}

# The value returned by this function is the statistical power of the experiment with your chosen parameters.
```

## Including Plots

You can also create plots, for example:

```{r}
#Let's look at how a range of effect sizes influence our power

#Make an empty vector to hold the results

power_results <- c()

#Make a range of effects you want to test -- here from .05 - 1, incrementing by .05
effect_range <- seq(from =.05, to = 1, by = .05)

# This for loop will store the results of each effect range iterratively in the results vector
for (i in 1:length(effect_range)) {
  print(paste("Running analysis for effect size", effect_range[i]))
  power_results[i] <- power_analyses(effect = effect_range[i], sample_size = 1000, yvar = 3, xmin = 0, xmax = 3)
}

# Combine the results and the input into a tibble that is easier to work with
power_stats <- tibble(effect = effect_range,
                        power = power_results)
power_stats #View tibble

#plot the results
ggplot(power_stats, 
       aes(x = effect, y = power)) +
  geom_line(color = 'red', size = 1.5) + 
  # add a horizontal line at 80%
  geom_hline(aes(yintercept = .8), linetype = 'dashed') + 
  theme_minimal() + 
  scale_y_continuous(labels = scales::percent) + 
  labs(x = 'Linear Effect Size', y = 'Power')
```
Okay, so this isn't great -- we need an effect size of ~ .3 to have good statistical power. Not impossible but not great either. Let's try the sample size instead.


```{r}

#Make a vector to store the results.
power_results <- c()

#Make a range of sample sizes -- this time from 1,000 samples to 20,000 samples, incrementing by 1,000
sample_range <- seq(from =1000, to = 20000, by = 1000)

#Mostly the same as before, simply switching the range to the sample_size parameter
for (i in 1:length(sample_range)) {
  print(paste("Running analysis for sample size", sample_range[i]))
  power_results[i] <- power_analyses(effect = .1, sample_size = sample_range[i], yvar = 3, xmin = 0, xmax = 3)
}

# Where do we cross 80%?
power_stats <- tibble(samples = sample_range,
                        power = power_results)
power_stats

ggplot(power_stats, 
       aes(x = samples, y = power)) +
  geom_line(color = 'red', size = 1.5) + 
  # add a horizontal line at 80%
  geom_hline(aes(yintercept = .8), linetype = 'dashed') + 
  theme_minimal() + 
  scale_y_continuous(labels = scales::percent) + 
  labs(x = 'Number of Samples', y = 'Power')

```
In order to get 80% statistical confidence with an effect size at .1 at the variances we see in our predictor/response, we need 10,000 samples. You can keep trying this with different distributions and variances to see how making your inputs more/less predictable will change you ability to achieve power.
